---
title: "The {esoph} dataset"
author: "Diandian Yi"
date: "12/9/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plotly)
library(tidyverse)
```

## General information 

The dataset {esoph} comes long in "R" package:

- The data comes from a case-control study of Espophageal Cancer in France
- Data was collected from 1175 patients with various age/alcohol/tobacco use combinations
- Among 1175 patients, 200 cancer "cases" are in cluded. Then 975 non-cases were samples from comparable hospital populations

## Description of the dataset

```{r description, echo = TRUE, message= FALSE}
sum(esoph$ncases) # 200 cancer "cases"
sum(esoph$ncontrols) # 1175 non-cases
str(esoph)
```

## Distribution of the observations for each age group

```{r agegp}
plot_ly(x = esoph$agegp, type = "histogram")
```

## how do the age and alcohol drinking impact getting cancer?

```{r percentage_age_alcohol, warning=FALSE, message=FALSE}
esoph_tibble <- esoph %>% as_tibble() %>% mutate(
  percentage_cases = ncases /(ncases + ncontrols) # convert to percentage 
) #construct the feature as the percentage of cancer cases in the dataset
plot_ly(esoph_tibble, x = ~agegp, y = ~percentage_cases, type = "scatter", color = ~alcgp, size = ~ncases)
```

## how do the age and tobacco impact getting cancer?

```{r percentage_age_tobacco, warning=FALSE, message=FALSE}
plot_ly(esoph_tibble, x = ~agegp, y = ~percentage_cases, type = "scatter", color = ~tobgp, size = ~ncases)
```

## 3D visualization

```{r 3D, warning=FALSE, message=FALSE}
plot_ly(esoph_tibble, x = ~alcgp, y = ~tobgp, z = ~percentage_cases, type = "scatter3d", color = ~agegp)
```